Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View

### 2020-07-20 Manuscript/sec2-review-of-graph-neural-network.tex
Update section 4.
修正了gaan的错误

						& \boldsymbol{g}_i = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_g}}(\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i}^{l, 2} \parallel \boldsymbol{s}_{i}^{l, 3}) \\
						& \boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_o}} (\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i} \odot \boldsymbol{s}_{i}^{l, 1}))

@@

		For Neural FPs, $\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}$ is the weight matrix for vertices with degree $|\mathcal{N}(i)|$ at layer $l$. 

>>>>

						& \boldsymbol{g}_i^l = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_g}}(\boldsymbol{h}_i^{l} \parallel \boldsymbol{s}_{i}^{l, 2} \parallel \boldsymbol{s}_{i}^{l, 3}) \\
						& \boldsymbol{h}_i^{l+1} = \textcolor{blue}{\boldsymbol{FC}_{\theta^l_o}} (\boldsymbol{h}_i^l \parallel (\boldsymbol{g}_{i}^l \odot \boldsymbol{s}_{i}^{l, 1}))

@@

		In Neural FPs, $\textcolor{blue}{\boldsymbol{W}}^{l, |\mathcal{N}(i)|}$ is the weight matrix for vertices with degree $|\mathcal{N}(i)|$ at layer $l$. 
